---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warnings = FALSE, 
  messages = FALSE, 
  prompt = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# getbatty  

Con-bat-tulations! This R package was adapted from the ohwhaley DIY R-package workshop, written by [fontikar](https://github.com/fontikar/ohwhaley), inspired by [cowsay](https://github.com/sckott/cowsay) and [praise](https://github.com/rladies/praise). I hope this package made you smile today! 

## First things first

`getbatty` is a toy project. Because I don't know how to use Git I'm not sure how to share it more widely than my computer - sorry!

## Usage

`getbatty` contains one function only. `say()` which will echo a randomly chosen bat-themed phrase for your enjoyment.

```{r example}
library(getbatty)
 
say() 
```

Alternatively, you can supply your own phrase

```{r, customise}
say("Hi, I'm Bat-thew McConaughey!")
```


